The \dealii Library, Version 9.7

### 2025-08-18 9.7/paper.tex
Minor updates.

In Figure~\ref{fig:tbb-vs-taskflow} we compare the time for assembling
the temperature matrix and temperature right-hand side in the step-32
tutorial program, like it was done in \cite{TKB16}. The test was performed
on a 3d mesh with 393,216 cells and 3,195,010 temperature degrees of freedom
using a $Q_2$ element. The tests are run
on AMD EPYC 9654P with 96 cores (and 192 threads). One can clearly see that
running all copy operations sequentially limits parallel scalability (to less than 10
threads on the left, where the copy operation is more expensive than the right),
while using graph coloring (denoted as ``colored'') eliminates this bottleneck.
It is clearly visible that the Taskflow implementation is better or the same
in all situations.

\begin{figure}[hb]
\includegraphics{kokkos-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{kokkos-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature matrix assembly, right: temperature right-hand side assembly) comparing TBB and Taskflow with and without coloring.}
\label{fig:tbb-vs-taskflow}
\end{figure}

>>>>

In Figure~\ref{fig:tbb-vs-taskflow} we compare the time for assembling
the temperature matrix and temperature right-hand side in the step-32
tutorial program, like it was done in \cite{TKB16}. The test was performed
on a 3d mesh with 393,216 cells and 3,195,010 temperature degrees of freedom
using a $Q_2$ element. The tests are run
on AMD EPYC 9654P with 96 cores (and 192 threads). One can clearly see that
running all copy operations sequentially limits parallel scalability (to less than 10
threads on the left, where the copy operation is more expensive than
the right), regardless of whether one uses the TBB or Taskflow. On the
other hand, first ``coloring'' all cells to avoid conflicts in
the copy operation (labeled as ``colored'' in the figure) eliminates this bottleneck.
It is clearly visible that the Taskflow implementation is better or the same
in all situations.

\begin{figure}[hb]
\includegraphics{kokkos-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{kokkos-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature
  matrix assembly, right: temperature right-hand side assembly)
  comparing TBB and Taskflow with and without coloring (corresponding
  to ``Implementation 2'' and ``Implementation 3'' in \cite{TKB16}).}
\label{fig:tbb-vs-taskflow}
\end{figure}
